Cover letter

### 2023-10-09 cover-letter.qmd
21 cover letter (#23)
* Add cover letter for #21

* Update cover letter

We are submitting our manuscript entitled "CRUSE to Safe Cycling in Ireland: An Open Source Tool to Support Active Travel" for consideration for publication in the European Transport Research Review.

@@

As a group we have wide experience in this space...

@@

>>>>

We are submitting our manuscript entitled "CRUSE to Safe Cycling in Ireland: An Open Source Tool to Support Active Travel" for consideration for publication in the European Transport Research Review.
It has a word count of 4,721, excluding references.

@@

As a group we have wide experience in this space, as highlighted by the below selection of our previous publications:

-   A paper on cycling safety based on route network analysis [@meade2018]

-   Methods enabling inequalities to be accounted for in cycle network analysis and design [@mahfouz]

-   Methods enabling accurate modeling and effective visualization of origin-destination data and route networks [@morgan2020; @lovelace2022]

-   Analysis of infrastructure preferences for cycling in Ireland [@caulfield2012]

-   Papers describing previous approaches to developing strategic cycle network planning tools [@lovelace2017]

@@

-   Highlight the open availability of the CRUSE tool to stakeholders in Ireland, increasing its use, leading to more evidence-based and likely more effective network level designs, accounting for trade-offs between investment in 'fast' vs 'quiet' networks

-   Increase awareness of open evidence to support effective and data-driven investment in and planning for cycling internationally

-   Provide information and inspiration to researchers and other stakeholders to imagine, explore, and in some cases invest time in developing new strategic cycle network planning tools

All the best,

Robin Lovelace on behalf of all authors, Joey Talbot, Eugeni Vidal-Tortosa, and Hussein Mahfouz (University of Leeds), Elaine Brick, Peter Wright, Gary O'Tool (AECOM), Dan Brennan and Suzanne Meade (Transport Infrastructure Ireland)

# References
